---
title: "Getting Started with PokemonAnalyzer"
author: "PokemonAnalyzer Contributors"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with PokemonAnalyzer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE
)

has_net <- function() {
  requireNamespace("curl", quietly = TRUE) && curl::has_internet()
}
```

PokemonAnalyzer is a lightweight R wrapper around the public PokéAPI. It provides simple functions to fetch Pokémon and move data, plus optional interfaces for: - an interactive GUI battle calculator (Shiny) - an interactive console team coverage tool

## Installation

```{r, eval=FALSE}
# install.packages("devtools")
# devtools::install_github("yueywangse/PokemonAnalyzer")
```

## Load the package

```{r load, eval=FALSE}
library(PokemonAnalyzer)
```

If you are developing locally inside the repo, use:

```{r load_all, eval=FALSE}
devtools::load_all()
```

## API wrapper basics

### List Pokémon

```{r list_pokemon, eval=FALSE}
if (has_net()) {
  head(pokeapi_list_pokemon(limit = 10))
}
```

### Fetch Pokémon details

```{r fetch_pokemon, eval=FALSE}
if (has_net()) {
  pika <- pokeapi_get_pokemon("pikachu")
  pika$name
  pika$types
  head(pika$stats)
}
```

### Fetch move details

```{r fetch_moves, eval=FALSE}
if (has_net()) {
  mv <- pokeapi_get_move("thunderbolt")
  mv$power
  mv$accuracy
  mv$type
  mv$damage_class
}
```

## GUI: Battle Calculator

PokemonAnalyzer includes a Shiny-based GUI battle calculator. This is an interactive feature, so we do not run it automatically inside the vignette.

```{r gui_source, eval=FALSE}
# run_gui()

## Console interface: Team Coverage (1-6 Pokémon)
```

PokemonAnalyzer also includes an interactive console tool that analyzes a team’s defensive and offensive type matchups using PokéAPI typing.

### Run the console tool

```{r, eval=FALSE}
# run_team_console()
```

The console interface will prompt you for 1-6 Pokémon names, then prints:

-   **Defensive multiplier matrix** (rows = attacking type, columns = your team)

-   **Types with no team resistance** (no Pokémon takes \<= 0.5x)

-   **Offensive multiplier matrix** (rows = defending type, columns = your team)

## Notes on offline use

These functions call the PokéAPI, so you need an internet connection.